---
title: "exploration3-questions"
author: "Duu Renn"
date: "September 9, 2016"
output: 
  pdf_document: 
    number_sections: yes
    toc: yes
---


------------

\vspace{3cm}

```{r source-530-exploration3, include=F}
tempR <- tempfile(fileext = ".R")
require(knitr)
# Let's make our paths work within the working directory for any machine
PROJHOME = normalizePath(getwd())
# purl(file.path(PROJHOME, "ps530", "exploration3.Rmd"), output=tempR) # Nope, it's broken
purl("C:/Users/duurenn2/Desktop/Dropbox/Graduate School/Fall 2016/uips-stat-share/ps530/exploration3.Rmd", output=tempR)
source(tempR)
unlink(tempR)
```


```{r setup-top-level, include=F}
require(knitr)
opts_chunk$set(
  tidy=TRUE,     # display code as typed # Changed to true because my comments are too long
  tidy.opts=list(width.cutoff=75),
  size="small",    # slightly smaller font for code
  echo=TRUE,
  results='markup',
  strip.white=TRUE,
  fig.path='figs/fig',
  cache=FALSE,
  highlight=TRUE,
  width.cutoff=132, 
  size='footnotesize',
  out.width='.9\\textwidth',
  fig.retina=FALSE,
  message=FALSE,
  warning=FALSE,
  comment=NA)
```

```{r packages, include=F}
# install.packages(c("devtools", "knitcitations"))
require(knitcitations)
cleanbib()
options("citations_format" = "pandoc")
```

__Questions__  
As people ask questions, I'll post responses here and push them to the shared folder. You can email me these questions or create an "issue" in the 'uips-stat-share' repository. Note that this is different than the 'explorations' repository -- we should probably try to keep that relatively clutter-free.  

# Readings
Before considering non-linear relationships, make sure that you have a good understanding of linear relationships and specifically how OLS fits its line. A closer reading (and practice) with the _Kaplan_ and _James et al_ textbooks should be useful here. Chapter 3 and the "Lab" section of the _James et al_ book should be especially helpful, as it also includes some topics that are useful for this week.  

