---
title: "exploration3-questions"
author: "Duu Renn"
date: "September 9, 2016"
output:
  html_document:
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
---


------------

/vspace{3cm}

```{r source-530-explorations, include=F}
require(knitr)
# I'm running all the R code from explorations 2 and 3 here. This way I'll have access to datasets and variables used in those assignments.
# To get this to work on your machine, you'll need to change the working directory. Look it up if you're interested!
setwd("C:/Users/duu/Documents/Dropbox/Graduate School/Fall 2016/uips-stat-share/")
source(purl("ps530/exploration2.Rmd"))
source(purl("ps530/exploration3.Rmd"))
```


```{r setup-top-level, include=F}
require(knitr)
opts_chunk$set(
  tidy=TRUE,     # display code as typed # Changed to true because my comments are too long
  tidy.opts=list(width.cutoff=75),
  size="small",    # slightly smaller font for code
  echo=TRUE,
  results='markup',
  strip.white=TRUE,
  fig.path='figs/fig',
  cache=FALSE,
  highlight=TRUE,
  width.cutoff=132, 
  size='footnotesize',
  out.width='.9//textwidth',
  fig.retina=FALSE,
  message=FALSE,
  warning=FALSE,
  comment=NA)
```

```{r packages, include=F, eval = F}
# install.packages(c("devtools", "knitcitations"))
require(knitcitations)
cleanbib()
options("citations_format" = "pandoc")
```

__Questions__  
As people ask questions, I'll post responses here and push them to the shared folder. You can email me these questions or create an "issue" in the 'uips-stat-share' repository. Note that this is different than the 'explorations' repository -- we should probably try to keep that relatively clutter-free.  

# Readings
Before considering non-linear relationships, make sure that you have a good understanding of linear relationships and specifically how OLS fits its line. A closer reading (and practice) with the __Kaplan__ and __James et al__ textbooks should be useful here. Chapter 3 and the "Lab" section of the __James et al__ book should be especially helpful, as it also includes some topics that are useful for this week.  

# Getting Started
Once you've read the textbook and worked through a few examplese, try returning to OLS using an example from class, but now with a continuous explanatory and outcome variable. As the exploration suggests, use the _age_ as your explanatory variable and support for Donald Trump (_fttrump_) as the outcome. You can find the codebook for this 2016 pilot of the ANES [here](http://www.electionstudies.org/studypages/anes_pilot_2016/anes_pilot_2016_CodebookUserGuide.pdf). If you don't know what a feeling thermometer is, look it up or ask an Americanist. Interested in the wording of the questions? Check [here](http://www.electionstudies.org/studypages/anes_pilot_2016/anes_pilot_2016_qnaire.pdf)/  

I put some code and comments below to help get you started


```{r}
# The variables
summary(anespi16$fttrump) # FT support for Donald Trump. Are there are surprising values?
summary(anespi16$birthyr) # Year born. Try to convert it into age.

# Fit the linear model, but exclude the 998s in the feeling thermometer
lmLinear <- lm(fttrump ~ birthyr, data=anespi16, subset=fttrump<=100)

# Guess: The greater your birthyear the lower your ft score for trump.
summary(lmLinear)
coef(lmLinear)
# Substantive interpretation
# refer to class notes

# Plot the data. Consider what line would fit? Would it fit well? What makes for a good and bad fit again, according to OLS? 
with(subset(anespi16, fttrump<=100), plot(birthyr, fttrump))
abline(a = 77, b= -.3, pch=4)

sum(lmLinear$residuals^2)

# Remeber the myssr() function? See if you can get it working for these data! A conus if you can get the contour plot working (no actual credit available).

# Here's an example of a contour plot using the ggplot package
require(ggplot2)

ggplot(data=faithfuld, aes(x=waiting, y=eruptions, z = density)) + 
  geom_contour()

```



